Joint estimation of SNP effects improves the prediction of complex diseases // Predicting complex diseases: performance and robustness [OF NEW METHOD?]

### 2018-04-02 paper/draft.tex
typo

We used three different ways to estimate the maximum achievable AUC for our simulations.
First, we used the estimation from equation (3) of \cite{wray2010genetic}. For a prevalence fixed at 30\% and an heritability of 50\% (respectively 80\%), the approximated theoretical values of AUC are 84.1\% (respectively 93.0\%). Note that this approximation is reported to be less accurate for high heritabilities.
Secondly, if we assume that the genetic part of the liabilities $y \sim N(0, h^2)$, we can estimate the theoretical value of the AUC that can be achieved given the heritability $h^2$ through Monte Carlo simulations. We report AUCs of 84.1\% and 94.1\% for respectively an heritability of 50\% and 80\%. [HOW TO ADD ERROR OF ESTIMATION? I HAVE SUMMARY() IN R]
Thirdly, we reproduce the exact same procedure of simulations and, for each combination of parameters (Table \ref{tab:simus}), we estimate the AUC of the ``oracle'', i.e.\ the true simulated genetic part of the liabilities though 100 replicates. For every combination of parameters, AUC of oracles are comprised between 83.2\% and 84.2\% for an heritability of 50\% and between 93.2\% and 94.1\% for an heritability of 80\%.
Given all these estimates of the maximal achievable AUC and for the sake of simplicity, we report maximum AUCs of 84\% (94\%) for heritabilities of 50\% (80\%) whatever are the parameters of the simulation.

>>>>

We used three different ways to estimate the maximum achievable AUC for our simulations.
First, we used the estimation from equation (3) of \cite{wray2010genetic}. For a prevalence fixed at 30\% and an heritability of 50\% (respectively 80\%), the approximated theoretical values of AUC are 84.1\% (respectively 93.0\%). Note that this approximation is reported to be less accurate for high heritabilities.
Secondly, if we assume that the genetic part of the liabilities $y \sim N(0, h^2)$, we can estimate the theoretical value of the AUC that can be achieved given the heritability $h^2$ through Monte Carlo simulations. We report AUCs of 84.1\% and 94.1\% for respectively an heritability of 50\% and 80\%. [HOW TO ADD ERROR OF ESTIMATION? I HAVE SUMMARY() IN R]
Thirdly, we reproduce the exact same procedure of simulations and, for each combination of parameters (Table \ref{tab:simus}), we estimate the AUC of the ``oracle'', i.e.\ the true simulated genetic part of the liabilities through 100 replicates. For every combination of parameters, AUC of oracles are comprised between 83.2\% and 84.2\% for an heritability of 50\% and between 93.2\% and 94.1\% for an heritability of 80\%.
Given all these estimates of the maximal achievable AUC and for the sake of simplicity, we report maximum AUCs of 84\% (94\%) for heritabilities of 50\% (80\%) whatever are the parameters of the simulation.
